### 2019-05-22 2-Chapters/1-Chapter/chapter1.tex
Added screenshots of the demo now hosted at https://perso.crans.org/besson/phd/MAB_interactive_demo/
My thesis is so long, and so stupid

% First chapter begins here
\chapter{Setting of This Thesis}
\label{chapter:1}
\minitoc

Abstract for Chapter 1.

@@

\tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
\begin{figure}[h!]
    \centering
    \resizebox{0.85\textwidth}{!}{
        \begin{tikzpicture}[auto,node distance=5cm,>=latex,scale=2]
            %
            % We start by placing the blocks
            \node [block] (player) at (0,0) {Player};
            % We draw an edge between the player and system block to
            \node [block] (environment) at (2,0) {Environment};
            % Once the nodes are placed, connecting them is easy.
            \draw [->] (player) to[bend left=90] node[pos=0.5] {Action} (environment);
            \draw [->] (environment) to[bend left=90] node[pos=0.5] {Reward} (player);
            %
        \end{tikzpicture}
    }
\caption{Reinforcement learning cycle.}
\label{fig:1:ReinforcementLearningCycle}
\end{figure}

@@

Here we discuss quickly the organization of the thesis.

\begin{figure}[h!]
    \centering
    \resizebox{0.85\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=3]
        %
        \node[align=center] (introduction) at (0,2.5) [rectangle,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2) [rectangle,draw] {Chapter~\ref{chapter:2}\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (4,2) [rectangle,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2,1) [rectangle,draw] {Chapter~\ref{chapter:4}\\Two MAB models for IoT networks};
        \node[align=center] (chapter5) at (0,1) [rectangle,draw] {Chapter~\ref{chapter:5}\\Multi-players MAB};
        \node[align=center] (chapter6) at (2,1) [rectangle,draw] {Chapter~\ref{chapter:6}\\Non-stationary MAB models};
        \node[align=center] (conclusion) at (0,0) [rectangle,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    }
    \caption{Organization of the thesis.}
    \label{fig:1:organization}
\end{figure}

@@

\begin{itemize}
\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}), Marrakech, Morocco, April 2019,
    \href{https://HAL.Inria.fr/hal-02006825}{\texttt{HAL.Inria.fr/hal-02006825}}.
    \cite{Besson2019WCNC}

\item
    \emph{Multi-Player Bandits Revisited},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory} (ALT, \href{http://www.cs.cornell.edu/conferences/alt2018}{\texttt{www.cs.cornell.edu/conferences/alt2018}}), Lanzarote, Spain, April 2018,
    \href{https://HAL.Inria.fr/hal-01629733}{\texttt{HAL.Inria.fr/hal-01629733}}.
    \cite{Besson2018ALT}

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \href{http://wcnc2018.ieee-wcnc.org}{\texttt{wcnc2018.ieee-wcnc.org}}), Barcelone, Spain, April 2018,
    \href{https://HAL.Inria.fr/hal-01705292}{\texttt{HAL.Inria.fr/hal-01705292}}.
    \cite{Besson2018WCNC}

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks} (CROWNCOM, \href{http://crowncom.org/2017}{\texttt{crowncom.org/2017}}), Lisboa, Portugal, Septembre $2017$,
    \href{https://HAL.Inria.fr/hal-01575419}{\texttt{HAL.Inria.fr/hal-01575419}},
    \textbf{Best Paper Award}.
    \cite{Bonnefoi17}

@@

% =============================================================================
\subsection{Publications in international conferences without proceedings}

@@

\item
    \emph{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation},\\
    by Christophe Moy \& \textbf{Lilian Besson}.
    1st International ISIoT workshop (\href{https://sites.google.com/view/ISIoT2019}{\texttt{sites.google.com/view/ISIoT2019}}),
    at \emph{Conference on Distributed Computing in Sensor Systems} (IEEE DCOSS, \href{http://2019.dcoss.org}{\texttt{2019.dcoss.org}}), Santorini, Greece, May 2019.
    \cite{MoyBesson2019}

\item
    \emph{Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions},\\
    by Rémi Bonnefoi, \textbf{Lilian Besson}, J. Manco-Vasquez \& Christophe Moy.
    1st International MOTIoN workshop (\href{https://sites.google.com/view/wcncworkshop-motion2019}{\texttt{sites.google.com/view/wcncworkshop-motion2019}}),
    at \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}), Marrakech, Morocco, April 2019.
    \cite{Bonnefoi2019WCNC}

\item
    \emph{MALIN: ``Multi-Arm bandit Learning for Iot Networks'' with GRC: A TestBed Implementation and Demonstration that Learning Helps},
    by \textbf{Lilian Besson}, Rémi Bonnefoi, Christophe Moy.
    Demonstration presented at \emph{International Conference on Communication} (ICT, \href{http://ict-2018.org/demos}{\texttt{ict-2018.org/demos}}), in Saint-Malo, France in June $2018$.
    See \href{https://YouTu.be/HospLNQhcMk}{\texttt{YouTu.be/HospLNQhcMk}} for a $6$-minutes presentation video.
    \cite{Besson2018ICT}

@@

% =============================================================================
\subsection{Submitted works}

\begin{itemize}
\item
    \emph{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires} (in French),
    submitted at GRETSI 2019, \href{http://GRETSI.fr/colloque2019}{\texttt{GRETSI.fr/colloque2019}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, March $2019$,
    \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019Gretsi}

@@

\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, February $2019$,
    \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019GLRT}

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \href{https://HAL.Inria.fr/hal-01840022}{\texttt{HAL.Inria.fr/hal-01840022}}.
    About $40000$ lines of code, hosted on \href{https://GitHub.com/SMPyBandits}{\texttt{GitHub.com/SMPyBandits}},
    with a complete documentation on \href{https://SMPyBandits.rtfd.io}{\texttt{SMPyBandits.rtfd.io}}.
    \cite{SMPyBandits,SMPyBanditsJMLR}

@@

\paragraph{Tutorial}
    I gave a tutorial\footnote{Cf. \href{HAL.Inria.fr/cel-01830248}{\texttt{HAL.Inria.fr/cel-01830248}}} on the Julia language, at IETR seminar in Vannes in June $2018$,
    with Pierre Haessig (\texttt{pierreh.eu}).

@@

\paragraph{Responsabilities}
    I was the president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \href{https://HAL.Inria.fr/hal-02013839}{\texttt{HAL.Inria.fr/hal-02013839}}}
    I also helped for the organization and presented another poster\footnote{Cf. \href{https://HAL.Inria.fr/hal-02013847}{\texttt{HAL.Inria.fr/hal-02013847}}} at the ``IETR : Interagir Evaluer Transmettre Réunir'' seminar, held in Vannes in June $2018$.

\paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning} (Lille) \href{https://ewrl.wordpress.com/ewrl14-2018}{\texttt{ewrl.wordpress.com/ewrl14-2018}}, in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \emph{NeurIPS} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.

>>>>

% First chapter begins here
\chapter{Introduction}
\label{chapter:1}
\minitoc

\paragraph{Abstract.}
We start by presenting the problems studied in this thesis,
then we announce the different directions we considered and the solutions we proposed.
We give an overview of our main contributions, alongside a list of publications written in the last three years.
\TODOL{Write this!}

@@

\tikzstyle{block} = [align=center, draw, fill=gray!25, rectangle, minimum height=3em, minimum width=6em]
\begin{figure}[h!]
    \centering
    \resizebox{0.40\textwidth}{!}{
        \begin{tikzpicture}[auto,node distance=5cm,>=latex,scale=2]
            %
            % We start by placing the blocks
            \node [block] (player) at (0,0) {Player};
            % We draw an edge between the player and system block to
            \node [block] (environment) at (2,0) {Environment};
            % Once the nodes are placed, connecting them is easy.
            \draw [->] (player) to[bend left=90] node[pos=0.5] {Action} (environment);
            \draw [->] (environment) to[bend left=90] node[pos=0.5] {Reward} (player);
            %
        \end{tikzpicture}
    }
\caption{Reinforcement learning cycle.}
\label{fig:1:ReinforcementLearningCycle}
\end{figure}

@@

Here we discuss quickly the organization of the thesis.
The manuscript is organized in two parts and six chapters, and the reading order can be any top-down path between Chapter~\ref{chapter:1} and the Conclusion in Chapter~\ref{chapter:conclusion}, in the graph shown in Figure~\ref{fig:1:organization} below.
In Part~\ref{part:Introduction}, we start by the next Chapter~\ref{chapter:2} where we introduce the MAB models, the concepts and the notations used in all this document, and it is mandatory to read it.
Conversely, Chapter~\ref{chapter:3} presents our simulation library SMPyBandits, and even if Chapters~\ref{chapter:2}, \ref{chapter:5} and \ref{chapter:6} use the library for their numerical simulation, reading this chapter is not required to understand the rest of the document.
%
Then the second Part~\ref{part:MABIOT} contain three chapters, that are included in both the logical and chronological orders, but can be read almost independently.
Chapter~\ref{chapter:4} starts by presenting different models of IoT networks where MAB algorithms have been used with success. Our two models are interesting and close to reality, but they appeared to be too general to propose a mathematical analysis of the good empirical performance of the considered solutions.
For this reason, we weaken the models for the rest of the document,
and both Chapters~\ref{chapter:5} and \ref{chapter:6} studies an intermediate model, lying between the stationary single-player MAB model from Chapter~\ref{chapter:2} and the IoT networks models from Chapter~\ref{chapter:4}.

\begin{figure}[h!]
    \centering
    % \resizebox{1.00\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=2.25]
        %
        \node[align=center] (introduction) at (0,3) [rectangle,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2) [rectangle,draw] {Chapter~\ref{chapter:2}\\Stochastic and Stationary\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (2.5,2) [rectangle,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2,1) [rectangle,draw] {Chapter~\ref{chapter:4}\\Two MAB models\\for IoT networks};
        \node[align=center] (chapter5) at (0,1) [rectangle,draw] {Chapter~\ref{chapter:5}\\Multi-players\\MAB models};
        \node[align=center] (chapter6) at (2,1) [rectangle,draw] {Chapter~\ref{chapter:6}\\Non-stationary\\MAB models};
        \node[align=center] (conclusion) at (0,0) [rectangle,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,densely dotted,<->]   (chapter4) to (chapter5);
        \draw [color=black,densely dotted,->]   (chapter3) to (chapter6);
        \draw [color=black,densely dotted,<->]   (chapter5) to (chapter6);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    % }
    \caption{Organization of the thesis: a reading map. Any path containing Chapter~\ref{chapter:1}, Chapter~\ref{chapter:2}, at least one of the three Chapters~\ref{chapter:4}, \ref{chapter:5} and \ref{chapter:6}, and the Conclusion is a self contained way to read this thesis.}
    \label{fig:1:organization}
\end{figure}

@@

\item
    \emph{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation},\\
    by Christophe Moy \& \textbf{Lilian Besson}.
    1st International ISIoT workshop\footnote{\href{https://sites.google.com/view/ISIoT2019}{\texttt{sites.google.com/view/ISIoT2019}}},
    at \emph{Conference on Distributed Computing in Sensor Systems} (IEEE DCOSS, \href{http://2019.dcoss.org}{\texttt{2019.dcoss.org}}), Santorini, Greece, May 2019.
    \cite{MoyBesson2019}

\item
    \emph{Upper-Confidence Bound for Channel Selection in LPWA Networks with Retransmissions},\\
    by Rémi Bonnefoi, \textbf{Lilian Besson}, J. Manco-Vasquez \& Christophe Moy.
    1st International MOTIoN workshop\footnote{\href{https://sites.google.com/view/wcncworkshop-motion2019}{\texttt{sites.google.com/view/wcncworkshop-motion2019}}},
    at \emph{Wireless Communication and Networks Conference} (IEEE WCNC, \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}), Marrakech, Morocco, April 2019.
    \cite{Bonnefoi2019WCNC}

\item
    \emph{GNU Radio Implementation of MALIN: ``Multi-Armed bandits Learning for Internet-of-things Networks''},
    by \textbf{Lilian Besson}, Rémi Bonnefoi \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{IEEE WCNC, \href{http://wcnc2019.ieee-wcnc.org}{\texttt{wcnc2019.ieee-wcnc.org}}}, Marrakech, Morocco, April 2019,
    \href{https://HAL.Inria.fr/hal-02006825}{\texttt{HAL.Inria.fr/hal-02006825}}.
    \cite{Besson2019WCNC}

\item
    \emph{Multi-Player Bandits Revisited},
    by \textbf{Lilian Besson} \& Emilie Kaufmann.
    \emph{Algorithmic Learning Theory}\footnote{ALT, \href{http://www.cs.cornell.edu/conferences/alt2018}{\texttt{www.cs.cornell.edu/conferences/alt2018}}}, Lanzarote, Spain, April 2018,
    \href{https://HAL.Inria.fr/hal-01629733}{\texttt{HAL.Inria.fr/hal-01629733}}.
    \cite{Besson2018ALT}

\item
    \emph{Aggregation of Multi-Armed Bandits learning algorithms for Opportunistic Spectrum Access},\\
    by \textbf{Lilian Besson}, Emilie Kaufmann \& Christophe Moy.
    \emph{Wireless Communication and Networks Conference}\footnote{IEEE WCNC, \href{http://wcnc2018.ieee-wcnc.org}{\texttt{wcnc2018.ieee-wcnc.org}}}, Barcelone, Spain, April 2018,
    \href{https://HAL.Inria.fr/hal-01705292}{\texttt{HAL.Inria.fr/hal-01705292}}.
    \cite{Besson2018WCNC}

\item
    \emph{Multi-Armed Bandit Learning in IoT Networks and non-stationary settings},
    by Rémi Bonnefoi, \textbf{Lilian Besson}, Christophe Moy, Emilie Kaufmann \& J. Palicot.
    \emph{Conference on Cognitive Radio Oriented Wireless Networks}\footnote{CROWNCOM, \href{http://crowncom.org/2017}{\texttt{crowncom.org/2017}}}, Lisboa, Portugal, Septembre $2017$,
    \href{https://HAL.Inria.fr/hal-01575419}{\texttt{HAL.Inria.fr/hal-01575419}},
    \textbf{Best Paper Award}.
    \cite{Bonnefoi17}

@@

% =============================================================================
\subsection{Demonstration in international conferences}

@@

\item
    \emph{MALIN: ``Multi-Arm bandit Learning for Iot Networks'' with GRC: A TestBed Implementation and Demonstration that Learning Helps},
    by \textbf{Lilian Besson}, Rémi Bonnefoi, Christophe Moy.
    Demonstration presented at \emph{International Conference on Communication}\footnote{ICT, \href{http://ict-2018.org/demos}{\texttt{ict-2018.org/demos}}}, in Saint-Malo, France in June $2018$.
    See \href{https://YouTu.be/HospLNQhcMk}{\texttt{YouTu.be/HospLNQhcMk}} for a $6$-minutes presentation video.
    \cite{Besson2018ICT}

@@

% =============================================================================
% \subsection{French language conference with proceedings}
\subsection{Submitted works}

\begin{itemize}
\item
    \emph{Analyse non asymptotique d'un test séquentiel de détection de ruptures et application aux bandits non stationnaires} (in French),
    submitted at GRETSI 2019\footnote{\href{http://GRETSI.fr/colloque2019}{\texttt{GRETSI.fr/colloque2019}}},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, March $2019$,
    \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019Gretsi}

@@

\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann, \\
    February $2019$,
    \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019GLRT}

\item
    \emph{SMPyBandits: an Open-Source Research Framework for Single and Multi-Players Multi-Arms Bandits (MAB) Algorithms in Python},
    by \textbf{Lilian Besson}, active development since October $2016$,
    \href{https://HAL.Inria.fr/hal-01840022}{\texttt{HAL.Inria.fr/hal-01840022}}.
    About $40000$ lines of code, hosted on \href{https://GitHub.com/SMPyBandits}{\texttt{GitHub.com/SMPyBandits}},
    and documentation on \href{https://SMPyBandits.rtfd.io}{\texttt{SMPyBandits.rtfd.io}}.
    \cite{SMPyBandits,SMPyBanditsJMLR}

@@

\paragraph{Tutorial}
    I gave a tutorial on the Julia language, at IETR seminar in Vannes in June $2018$,
    with Pierre Haessig (\texttt{pierreh.eu}), see \href{https://HAL.Inria.fr/cel-01830248}{\texttt{HAL.Inria.fr/cel-01830248}}.

@@

\paragraph{Responsabilities}
    I was the president of the PhD Students Association of IETR lab (ADDI, \texttt{addi.asso.insa-rennes.fr}) in $2017$.
    I was notably in charge of organizing the PhD Students day at Rennes, in June $2017$, with about $350$ people, and presentation of a research poster\footnote{Cf. \href{https://HAL.Inria.fr/hal-02013839}{\texttt{HAL.Inria.fr/hal-02013839}}}
    I also helped for the organization and presented another poster\footnote{Cf. \href{https://HAL.Inria.fr/hal-02013847}{\texttt{HAL.Inria.fr/hal-02013847}}} at the ``IETR : Interagir Évaluer Transmettre Réunir'' seminar, held in Vannes in June $2018$.

\paragraph{Reviews}
	for \emph{European Workshop on Reinforcement Learning}\footnote{Cf. \href{https://ewrl.wordpress.com/ewrl14-2018}{\texttt{ewrl.wordpress.com/ewrl14-2018}}} (Lille), in October $2018$, I reviewed $5$ papers.
	I helped colleagues for articles submitted at international conferences \emph{AISTATS} $2019$, \emph{NeurIPS} $2017$ et $2018$, and \emph{COLT} $2018$ and $2019$, for about 10 \emph{reviews}.
